\clearpage
\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

The usage of spreadsheet in daily basis, usually used as a data collector. Spreadsheet is one of the easy to use software, so that many people prefer it as data management software than using a proper database management system. This could causing so many problems because the spreadsheet itself is not design to be a data collector. Some problem presisted as people use is as data collector, such as no data validation, isolation of data, and hard to collaborate. In order to solve those problem, this final year project want to create a spreadsheet software that could integrate with existing database and synchronize it with the data in the spreadsheet, could verify the data, and easy to collaborate.

This report will cover the analysis behind the software requirement in order to get the integrated software with the database. This will include data transformation with 4 steps, clustering, row identification, cell identification, and header-data assignment. This software is using two machine learning algorithm in order to do a proper transformation, the Hierarchical Clustering and Conditional Random Field. The training data set is from Statistical Abstract of the United States (SAUS) 2010 and some manual data gathering. The next step is validation, this software will cover 3 type of validation, such as data type, data domain, and data relation. Those algorithm build on top of an open source spreadsheet software called EtherCalc which already could do online collaboration.

Keyword: spreadsheet, data collector, data quality, data management.
\clearpage